3D-printable micropipette

### 2015-01-26 publishing/plos_template.tex
started discussion

% Results and Discussion can be combined.
\section*{Results}

% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}

>>>>

% Results and Discussion can be combined.
\section*{Results and Discussion}

Our printed pipette had a comparable accuracy to a commerical pipette (table 1).
The commerical pipette has a digitial readout that allows the user to adjust precisly to set values where the printed pipette is adjusted by eye according to graduations.
This is certianly the cause of the lower accuracy and wider deviation although it's preforamce is impressive.

The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurments without validating with a scale (Figure3).
% We only support three levels of headings, please do not create a heading level below \subsubsection.
\subsection*{Subsection 1}
